Correlation among smart grid actors

### 2015-05-18 Article.tex
update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Abstract
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Achieving a successful energetic transition became a major goal for the 21st century in most developped countries. The reconciliation of several research areas and their recent focus on the same smart grid objective has led to major technical improvements. For instance, allowing large penetrations of renewables into the electricity production seemed more like a dream yesterday, but appears more and more doable as research progresses. The inherent volatility of some of these energy sources poses indeed various problems in such a constrained environment. It is often supposed that a large number of these small generators will be decentralized down to the distribution networks and even be owned by individuals. By enabling bi-directional flows, this vision revolutionises the nature of the simple todays's consumer into some futuristic agent that both consumes and produces. It is often considered that these individual productions will be used only to meet the agent own demand (in real time or through batteries).

In this paper, we consider agents that tend to produce more than they consume and seek to sell their surplus of production. More precisely, we rely on aggregations of these agents that can be seen as virtual power plants with production and consumption components that are both variable. Because these virtual power plants are complex aggregations of different types of production means and consumption habits, the volatilities of the plants productions are deeply impacted by the correlation between the agents. We propose here an algorithm that takes the underlying correlation structure of the agents into account while forming the coalitions. We show then that the resulting diversified coalitions are able to generate higher benefits on a constrained energy market, and are more resilient to random failures of the agents.
\end{abstract}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Abstract
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Achieving a successful energetic transition became a major goal for the 21st century in most developped countries. The reconciliation of several research areas and their recent focus on the same smart grid objective has led to major technical improvements. For instance, allowing large penetrations of renewables into the electricity production seemed more like a dream yesterday, but appears more and more doable as research progresses. The inherent volatility of some of these energy sources poses indeed various problems in such a constrained environment. It is often supposed that a large number of these small generators will be decentralized down to the distribution networks and even be owned by individuals. By enabling bi-directional flows, this vision revolutionises the nature of the simple today's consumer into some futuristic agent that can both consume and produce. Such an agent can obviously reduce its electricity bill by seeking energetic independance through demand side management programs coupled with storage. Nevertheless, as it could be the case that an agent's production exceeds its consumption and storage capacity, its ability to sell its extra-production appears as a way to save energy.

In this paper, we thus consider agents that tend to produce more than they consume and seek to sell their surplus of production. More precisely, we rely on aggregations of these agents that can be seen as virtual power plants with production and consumption components that are both variable. Because these virtual power plants are complex aggregations of different types of production means and consumption habits, the volatilities of the plants productions are deeply impacted by the correlation between the agents. We propose here an algorithm that takes the underlying correlation structure of the agents into account while forming the coalitions. We show then that the resulting diversified coalitions are able to generate higher benefits on a constrained energy market, and are more resilient to random failures of the agents.
\end{abstract}

@@

In this paper we studied how aggregations of prosumers could be authorized to sell their surplus of production to the grid operator. By relying on the past values of the agents, we constrained the market entry to both sufficiently productive and stable coalitions. The power that a coalition is able to propose on the market is therefore related to both quantities. As the correlations between the prosumers that form these coalitions impact directly their volatilities, we seek uncorrelated aggregations of agents. We used a greedy algorithm that starts with cliques of the "de-correlation" graph of the agents and makes local improvements. We compare the results with a random search and an opposite strategy that clusters correlated agents together. We showed that the coalitions resulting from our algorithm are able to provide more stable power to the grid because they tend to have globally better production over volatility ratios while the others are generally more disparate.

Because in real situations, agents are prone to failure, the resilience of the coalitions is an important criterium. We therefore studied how the coalitions are able to remain on the market when their agents fail randomly one by one. We showed that, in this situation, the coalitions resulting from our algorithm better withstand losses of agents.
